---
title: "Days Until Report Due"
author: "me"
date: "November 6, 2023"
output: pdf_document
---

# Days Until Report Due

This file contains three code chunks in R that will determine the number of days until my PU5058 report is due:

1.  The first code chunk will get and return the current date from the local system.

2.  The second code chunk will set and return the date that the PU5058 report is due.

3.  The third code chunk will calculate the difference, in days, between today's date and the due date of the PU5058 report.

## Create the variable "today" and assign it to today's date.

```{r}
today <- Sys.Date()
print(today)
```

Variables:

-   today

Functions:

1.  Sys.Date() function to get the current date according to the local system

2.  print() function used to print results

## Create variable "reportDate" and set it to November 21, 2023

```{r}
  reportDate <- "2023-11-21"
  print(reportDate)
```

Variables:

-   reportDate

Functions:

1.  print() function used to print results

## Calculate Days until PU5058 Report Due

```{r}
diff_dates = difftime(as.Date(reportDate), as.Date(today), units = "days") 

diff_dates = as.numeric(diff_dates)

print(paste(diff_dates," days until PU5058 report is due!!"))
```

Variables:

-   reportDate (from code chunk 2)

-   today (from code chunk 1)

Functions:

1.  as.Date() function used to format dates

2.  difftime() function used to calculate date differences

3.  as.numeric() function used to extract only the numerical value of the difftime function output

4.  print() function used to print the message containing number of days left until the report is due

5.  paste() function used to concatenate the numerical value obtained in the difftime function and the desired text of my output message.

## Checklist

-   [x] Section headers

-   [x] 1 Unordered list (checklist)

-   [x] 1 Numbered list (more than 1)

-   [x] Two Code Chunks (more than 2)
